Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-11 cbm-rbd-paper.tex
better plot with rel and gnow
figure caption update

\begin{figure}
\includegraphics[width=\textwidth]{ghistfig1}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghistfig1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig2}
\caption{$\tausnow$, $t^* = \tnow + \tausnow$ and $\gnow(\tausnow)$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
dropping at each component failure.
If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
at (absolute) time $8.5$.
As $\tausnow$ does not change dramatically most of the time, $t^*$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
differing from the overall cost rate (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At time $8$, the overall expected cost rate for repair at time $8.38$ is $0.314$,
up from $0.076$ for repair at time $8.62$, as cost-optimal at time $8$.}
\label{fig:tauhistfig2}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{ghistfig2}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghistfig2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig2}
\caption{$\tausnow$, $t^* = \tnow + \tausnow$, $\gnow(\tausnow)$, and the total cost rate **** as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
at (absolute) time $8.5$.
Since $\tausnow$ does not change dramatically most of the time, $t^*$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
differing from the overall cost rate (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At time $8$, the overall expected cost rate for repair at time $8.38$ is $0.314$,
up from $0.076$ for repair at time $8.62$, as cost-optimal at time $7.9$.}
\label{fig:tauhistfig2}
\end{figure}
